Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2018-10-17 tex/WW4C_VHzQ.tex
Small changes
VSA notes updated

In this paper we include all non-proprietary WFCAM data, which covers all
public surveys and PI projects from Semester 05A to 1st January 2017, and all
non-proprietary VISTA data, which covers all public surveys and PI projects from
science verification (20091015) to 1st April 2016.

@@

We query the WSA and VSA performing matched-aperature photometry at
the positions of our 424 VH$z$Qs. We return a database with $xxxx$
entries. This database is world-readable and we give the full receipe
and relevant SQL queries in Appendix~\ref{sec:SQL}.

@@

    We calculate a set of averaged catalogues, for each pointing and filter, based
    on the requirements in \verb+RequiredMapAverages+, in these cases over time
    spans of 7, 14, 30, 91, 183 days, 365 days, 730 days, over 10 epochs and over all epochs,
    see Tab.~\ref{tab:reqMapAvg}. The
    averaging process starts at the first epoch and works on.
    %%
    We give examples of the SQL queries syntax in Appendix~\ref{sec:SQL}.

    114 quasars have both WFCAM and VISTA data.

@@

\section{Near-Infrared WFCAM Science Archive SQL queries}\label{sec:SQL}
Here we give the receipe and SQL that returned the near-infrared photometry 
for the VH$z$Qs.

@@

Second, the {\tt RA} and {\tt DEC} values returned by the WSA are in radians.

\onecolumn
\input{SQL_examples}
\twocolumn

>>>>

We access both the WSA and the VSA and include all non-proprietary WFCAM data, which covers all
public surveys and PI projects from Semester 05A to 1st January 2017, and all
non-proprietary VISTA data, which covers all public surveys and PI projects from
science verification (20091015) to 1st April 2016.

@@

We query the WSA and VSA performing matched-aperature photometry at
the positions of our 424 VH$z$Qs. We return a database with $xxxx$
entries. This database is world-readable and we give the full receipe
and relevant SQL queries for accessing both databases in Appendix~\ref{sec:SQL}.

@@

    We calculate a set of averaged catalogues, for each pointing and filter, based
    on the requirements in \verb+RequiredMapAverages+, in these cases over time
    spans of 7, 14, 30, 91, 183 days, 365 days, 730 days, over 10 epochs and over all epochs,
    see Tab.~\ref{tab:reqMapAvg}. The
    averaging process starts at the first epoch and works on.

    We detect 304 unique quasars in the WFCAM WSA database, 203 quasars are detected in the VISTA VSA database with 114 objects in common with both WFCAM and VISTA data. We give the necessary SQL queries syntax in Appendix~\ref{sec:SQL}.

@@

\section{Near-Infrared WFCAM Science Archive SQL queries}\label{sec:SQL}
Here we give the receipe and SQL that returned the near-infrared photometry 
for the VH$z$Qs from the  WFCAM Science Archive.

@@

Second, the {\tt RA} and {\tt DEC} values returned by the WSA are in radians, if
used directly. To return values in degrees, use a selection with an alias, e.g. 
{\tt RA as RADeg} and {\tt DEC as DECDeg}.

\onecolumn
\input{SQL_examples_WSA}
\twocolumn

\section{Near-Infrared VISTA Science Archive SQL queries}\label{sec:SQL}
In a very similar manner to the WSA, we give here the details on how to access
the VISTA Science Archive (VSA)

At the \href{http://horus.roe.ac.uk/vsa/login.html}{VSA Login}, enter 
with these credentials::
\begin{itemize}
    \item Username: {\tt VSERV1000} 
    \item password: {\tt highzqso} 
    \item community: {\tt proprietary}
\end{itemize}
Then head to the \href{http://horus.roe.ac.uk:8080/vdfs/VSQL_form.jsp}{Freeform SQL Query} page where the database release to use is {\tt VSERV1000v20180716}.

\onecolumn
\input{SQL_examples_VSA}
\twocolumn
